%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
{University of Washington, eScience Institute}
{Data Scientist}
{April 2018 - Present}
{Seattle, WA}
{
  \begin{cvitems}
    \item{Lead Data Scientist, providing technical mentoring to an interdisciplinary team to assess, map and analyze access to out-of-school resources for students in Denver, CO.} %\href{http://35.167.60.237:3838/osr_dssg2018/RShiny/app/}{\underline{\textit{product}}}}
    \item{Create and teach workshops on open source tools (R and Python) to greater University and sorrounding community}
  \end{cvitems}
}
%---------------------------------------------------------
  \cventry
  {Community Center for Education Results}
  {Data Scientist}
  {January 2017 - March 2018}
  {Seattle, WA}
  {
    \begin{cvitems} 
      \item {Leveraged predictive analytics and machine learning techniques to drive strategic decision-making and continuous improvement efforts for education outcomes in the region. \href{https://docs.google.com/presentation/d/1hXTSttTE6oddJywVadC25Lxk6259VEPO2anXnqbrSZ4/edit?usp=sharing}{\underline{\textit{example}}}}
      \item {Defined KPIs, and use-cases for data products. (i.e. Interactive dashboards using SQL-R-Tableau).}
      \item {Designed and standardized methods to retrieve, integrate, and aggregate data from disparate sources thereby optimizing the data collection processes for future projects. \href{https://github.com/CCER-RMP/S275_ETL}{\underline{\textit{example}}}}
    \end{cvitems} 
  }

%---------------------------------------------------------
  \cventry
  {Insight Data Science}
  {Postdoctoral Fellow}
  {Jan. 2016 - July 2016}
  {Seattle, WA}
  {
    \begin{cvitems}
      \item {Consulted with startup CEO and communicated technical results/methods that lead to actionable insights used by the company to improve their product.}
      \item {Mined 300-million user database using PostgreSQL, R and Python to determine mobile phone app user audience segments for advertiser clients using Machine Learning clustering techniques. \href{https://youtu.be/QwjuLMO930E}{\underline{\textit{example}}}}
    \end{cvitems}
  }
 %---------------------------------------------------------
 \cventry
 {University of Washington}
 {Research Scientist}
 {June 2015 - December 2016}
 {Seattle, WA}
 {
   \begin{cvitems}
     \item{Lead data analyst on various on-going grant projects.  From design to data collection/management, to analysis and reporting.}
     \item{Created statistically matched comparison samples for quasi experimental intervention studies.}
     \item{Communicated technical results that helped collaborators, stakeholders, and funding agencies from varying multidisciplinary backgrounds determine the efficacy of their investments.}
     \item{Develop interactive workshops to help research organizations transition to open-source technologies (R and Git) for collaborative data analyses and reporting.}
   \end{cvitems}
 }

%---------------------------------------------------------

\end{cventries}
