\cvsection{Experience}

\begin{cventries}
	\cventry
		{Community Center for Education Results (non-profit)}
    	{Data Scientist}
    	{January 2017 - Present}
    	{Seattle, WA}
    	{
      		\begin{cvitems} 
      			\item {Leveraged predictive analytics and machine learning techniques to drive strategic decision-making and continuous improvement efforts for education outcomes in the region. \href{https://docs.google.com/presentation/d/1hXTSttTE6oddJywVadC25Lxk6259VEPO2anXnqbrSZ4/edit?usp=sharing}{\underline{\textit{example}}}}
      			\item {Defined KPIs, and use-cases for data products. (i.e. Interactive dashboards using SQL-R-Tableau).}
      			\item {Designed and standardized methods to retrieve, integrate, and aggregate data from disparate sources thereby optimizing the data collection processes for future projects. \href{https://github.com/CCER-RMP/S275_ETL}{\underline{\textit{example}}}}
      		\end{cvitems} 
    	}

 	\cventry
	{Insight Data Science}
	{Postdoctoral Fellow}
	{Jan. 2016 - July 2016}
	{Seattle, WA}
	{
	\begin{cvitems}
		\item {Consulted with startup CEO and communicated technical results/methods that lead to actionable insights used by the company to improve their product.}
		\item {Mined 300-million user database using PostgreSQL, R and Python to determine mobile phone app user audience segments for advertiser clients using Machine Learning clustering techniques. \href{https://youtu.be/QwjuLMO930E}{\underline{\textit{example}}}}
	\end{cvitems}
	}
   \cventry
    {University of Washington}
    {Research Scientist}
    {June 2015 - December 2016}
    {Seattle, WA}
    {
      \begin{cvitems}
        \item{Lead data analyst on various on-going grant projects.  From design to data collection/management, to analysis and reporting.}
 %       \item{Designed and standardized methods to retrieve, integrate, and aggregate data from disparate sources.}
        \item{Created statistically matched comparison samples for quasi experimental intervention studies.}
        \item{Communicated technical results that helped collaborators, stakeholders, and funding agencies from varying multidisciplinary backgrounds determine the efficacy of their investments.}
        \item{Develop interactive workshops to help research organizations transition to open-source technologies (R and Git) for collaborative data analyses and reporting.}
      \end{cvitems}
    }
  \cventry
    {University of Washington}
    {Grad Research Assistant - Quantitative Analyst}
    {July 2010 - June 2015}
    {Seattle, WA}
    {
      \begin{cvitems}
        \item{Collected, cleaned, and managed large-datasets from various sources.}
        \item{Build data visualization prototypes in R for quarterly/yearly reports.}
        \item{Collaborated as the lead quantitative analyst with social science researchers on 5 peer reviewed publications.}
        \item{Conducted Monte Carlo experiments to assess the performance of quasi-experimental matching based methods on complex data structures}
      \end{cvitems}
    }

%    \cventry
%{Private Practice}
%{Applied Statistics Consultant}
%{January 2015 - Present}
%{Seattle, WA}
%{
%	\begin{cvitems}
%		\item{Have served as a statistical consultant on over 20 dissertation/grants proposals \& projects for CBO's, graduate students and faculty.}
%		\item{Created a data-driven decision making culture by developing infrastructure for data collection and evaluation of flagship recruitment programs at the University of Washington, leveraging multiple data sources and other assets, leading to improved recruitment products.}
%		\item{Develop survey instruments for data collection and validation protocols for projects at all phases of implementation.}
%		\item{Develop interactive workshops to help research organizations transition to open-source technologies (R and Git) for collaborative data analyses and reporting.}
%	\end{cvitems}
%}
%  \cventry
 %   {University of Washington, Department of Statistics}
   % {Teaching Assistant, Bayesian Statistics \& Hierarchical Linear Models}
   % {Mar. 2014 - June 2015}
    %{Seattle, WA}
    %{
      %\begin{cvitems}
        %\item{Communicated complex statistical theories and results to graduate students representing different departments.}
        %\item{Developed example code and solutions in R for lectures and problem sets.}
      %\end{cvitems}
    %}
   \end{cventries}
